%----------------------------------------------------------------------------------------
%	CHAPTER - LITERATURE REVIEW
%----------------------------------------------------------------------------------------

\chapter{Literature Review} % Main chapter title

\label{ChapterLiteratureReview} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

In the literature review chapter, an overview of existing research found in secondary literature, that is relevant to the thesis statement of this paper, is given. Every \gls{srq} is discussed in its own subchapter where its relevance to the \gls{mrq} is elaborated. Each subchapter ends with a short conclusion and answers to the corresponding research question are given.
Figure XXX shows the correlation between the subchapters and the research questions. In chapter \ref{SectionLiteratureReviewSRQ1}, XXXX. The next chapter \ref{SectionLiteratureReviewSRQ2} XXXX. By XXXXX, the third SRQ is covered in chapter \ref{SectionLiteratureReviewSRQ3}. To wrap everything up, a conclusion of the literature review is presented in chapter \ref{SectionLiteratureReviewConclusion} which builds the base for the research design in chapter \ref{Research Method}.

% TODO: ADD FIGURE AND COMPLETE


%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Existing Interaction Patterns with Virtual Reality}

\label{SectionLiteratureReviewSRQ1}

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Introduction}

\gls{hci} itself has been worked and research on approximately from the 1950s onwards, where the main focus was on the direct manipulation of graphical objects, the mouse as well as gesture recognition \citep{Myers1998}. During this time however, gesture recognition was rather undertood as devices that work with pen-based input devices and thus can recognize patterns that are drawn with these pens \citep{Myers1998}.


%-----------------------------------
%	SUBSECTION 2
%-----------------------------------

\subsection{Overview}

blub

The force feedback subsystem uses robotic positioning to place an assortment of knobs and switches into position to be touched; the user's hand trajectory is extrapolated and the correct type of control is placed just in time to be actuated.
\cite{Latham1997}

A system for the visualization of three-dimensional anatomical data, derived from magnetic resonance imaging (MRI) or computed tomography (CT), enables the physician to navigate through and interact with the patient's 3D scans in a virtual environment. This paper presents the multimodal human-machine interaction focusing the speech input. For the concerned task, a speech understanding front-end using a special kind of semantic decoder was successfully adopted
\cite{Muller1998}

We highlight results drawn from a study on pointing and draw conclusions for the implementation of pointing-based conversational interactions in partly immersive virtual reality.
\cite{Pfeiffer2008}

Oculus Rift can track head movement and change view point follow it. Leap Motion is in - air controller that can track hand gesture of the user. The combination of them will make users feel like immerse to VR. Users can move avatar any way in VR by their hand interact through the system via these devices. We introduce a new interactive hand gesture system with palm normal for control steering develop by the game engine Unity3D applies synchronization of Oculus Rift and Leap Motion.
\cite{Khundam2015a}

It allows user to interact with the virtual reality system with the static and stroke hand gesture along with speech. This multimodal interaction technique is able to perform few functions such as select, move, scale, rotate, copy, mirror, delete, check the shape, check and change the colour of an object.
\cite{Chun2015}

There are some limitations of the multimodal interaction. For example, when the hand is not tracked properly, the stroke gesture recognizer cannot recognize the stroke gesture command. User also has to perform the stroke command in certain speed level. The
\cite{Chun2015}


%-----------------------------------
%	SUBSECTION 3
%-----------------------------------

\subsection{Visual Information Seeking Mantra}

blub



%-----------------------------------
%	SUBSECTION 4
%-----------------------------------

\subsection{Conclusion}

blub



%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{SRQ 2}

\label{SectionLiteratureReviewSRQ2}

blub



%----------------------------------------------------------------------------------------
%	SECTION 3
%----------------------------------------------------------------------------------------

\section{SRQ 3}

\label{SectionLiteratureReviewSRQ3}

blub




%----------------------------------------------------------------------------------------
%	SECTION 4
%----------------------------------------------------------------------------------------

\section{Conclusion}

\label{SectionLiteratureReviewConclusion}

blub

