%----------------------------------------------------------------------------------------
%	CHAPTER - CONCLUSION
%----------------------------------------------------------------------------------------

\chapter{Conclusion}

\label{ChapterConclusion}

The final chapter in this thesis covers the final phase of the \gls{dsr} cycle from \cite{Vaishnavi2008}, the \textit{Conclusion}. They classify this phase as the one where the results of the effort is consolidated and the knowledge gained categorized and documented \citep{Vaishnavi2008}.


%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Introduction}

In the first part of the conclusion, a summary of the research done in this thesis is provided. Then the main findings of the literature review and the design, implementation and evaluation of the prototype application are provided, as well as an answer to the \gls{mrq} from the first chapter. Finally, a suggestion for future research is given.


%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{Summary}

Beginning with the problem statement that information about the personal financial situation is till presented in the same ways like a decade ago, and that only little research has been made in how to visualize data in \gls{vr}, this thesis proposed a solution approach to close this gap. With the first \gls{srq}, research about the different methods of user input in \gls{vr} was conducted, which showed their individual advantages and disadvantages compared with others. Next, with the second \gls{srq} the focus was on different interaction patterns of \gls{vr} where a classification into \textit{Travel}, \textit{Selection}, and \textit{Manipulation} can be found. The \gls{vism} give some more guidelines in what tasks should be available to the user for an effective information seeking. With the third \gls{srq}, different approaches for the visualisation of data in \gls{vr} have been analysed and a close relation to the type of data could be seen. Alongside the \textit{Suggestion} phase of the \gls{dsr} cycle where a design for a prototype application is proposed, a first part of \gls{srq} is discussed in terms of what the potential benefits can be by bringing the interaction with categorized financial data into \gls{vr}. Building up on that, the \textit{Development} and \textit{Evaluation} phase confirmed the technical feasibility of the proposed design and showed its effectiveness in a set of different scenarios. Since the prototype is much more limited in terms of filtering possibilities, the evaluation is heavily depending on the scenario. With the right focus, the prototype clearly beats the current e-banking solution in terms of effectiveness and comprehensibility. In other cases it is somewhat sub-par to the traditional e-banking solution but still is able to allow for a successful completion of the desired task.


%----------------------------------------------------------------------------------------
%	SECTION 3
%----------------------------------------------------------------------------------------

\section{Findings}

The following findings were made during the thesis:
\begin{itemize}[]
	\item noitemsep = off
	\item nolistsep = off
\end{itemize}


With respect to the thesis statement, it can be said that the level of enhancement is depending on the specific scenario of the exploratory analysis. Due to the multiple linked views, the prototype can show its strengths when the scenario asks for switches in these views, such as comparing one month with another which can be done with just one click in the prototype application whereas in e-banking the selected date-range has to be manually adjusted. Contrary to that, with a very detailed question the prototype comes soon to its limitations as in its current state it only supports a filtering for categories and full years/months/days, but not for individually defined date-ranges or any other criteria such as amount-ranges or account selection. This however does not mean that the answer cannot be found with the prototype as well, it is just not as effective to do so as with other scenarios.
\begin{framed}
	\textit{\thesisstatementtext}
\end{framed}

Based on these results, the thesis statement as defined above, is not rejected.




-----------------------------

The purpose of a conclusion is to answer your research question. Begin, with repeating your research question. However, don’t simply reiterate the research question, but integrate an explanation of it into the rest of the section’s discussion.

Then give the conclusions that you draw based on the results of your research (use the key results that are most relevant for answering your research question).

Finally, answer the main question and explain how you have come to this conclusion. Don’t just list the question with the answer below it, but carefully explain it and incorporate it into the rest of the text. Provide the raw observations and don’t interpret.

-----------------------------


The conclusion typically covers the following:

What was learned (this usually comes first)
What remains to be learned (directions for future research)
The shortcomings of what was done (evaluation)
The benefits, advantages, applications, etc. of the research (evaluation)
Recommendations


This basic pattern might help in terms of structure

Start para/mini-section with a summary of what was DONE ("I conducted an analysis of ABC)
Move into what was FOUND in terms of your analysis ("From this analysis, XYZ became apparent" -- this is also a 'summary')
Draw out implication 1, implication 2, etc. ("because of XYZ, we can now say PQR which leads to KLM")

THEN

Point to any gaps/problems ("However, we CANNOT say DEF")
And then to what needs to be done next ("So therefore we should look at GHI")
I have run out of alphabet.




%----------------------------------------------------------------------------------------
%	SECTION 4
%----------------------------------------------------------------------------------------

\section{Future Research}

With regards to the different \glspl{srq}, future research in the following areas could lead to new knowledge for the academic community and help on further improving the prototype application.
\begin{itemize}[]
	\item \textbf{\gls{srq} 1:} As mentioned in the findings, the weaknesses of the prototype application are related to very specific queries that have to be executed. As an alternative to just provide more buttons and input fields in the \gls{ve} with the risk of overloading it, the utilization of \textit{Speech Recognition} integrated in the \gls{vr} application could potentially generate massive improvements. More advanced filtering such as "Show me all transactions over CHF 100 in the last seven days" would become possible.
	
	\item \textbf{\gls{srq} 2:} From the \gls{vism} 2.0, only the main tasks were considered for this thesis, whereas the three support tasks \textit{History}, \textit{Extract}, and \textit{Collaboration} were not in focus. Especially the \textit{Collaboration} support task could allow for even better exploratory analysis when the \gls{ve} is shared with additional people. In terms of practical relevance, this could allow to have the client advisor in the same (virtual) room as the client to discuss the financial situation more collaboratively.
	
	\item \textbf{\gls{srq} 3:} In the current design, the actual financial transactions are only shown as part of a table. Additional exploratory analysis possibilities could be created by looking into the concept of the 'data forest' again. With a 3D visualisation of the individual transactions, new insights into the data might be found.
	

\end{itemize}

	\srqfourtext
	
With the given artefact STD – the author sees multiple areas where future research in connection with the findings of this thesis resp. with the use of STD itself can lead to new knowledge for the academic community. The following sections explain shortly the field of possible research for each area.

tbd

SRQ 1: speech recognition (e.g. Show me all transactions in the last seven days over CHF 100.) \newline
SRQ 2: Include Support Tasks from VISM \newline
SRQ 3: data forest for individual transactions \newline
select multiple months/days for the list of transactions \newline
include sub-categories \newline
evaluate with other banking products  \newline




